### 2022-09-10 main/chapter_searches.tex
add another p-value criticism

% p-values
\TODO{no!}~\cite{
schervish1996p,
Cohen1994TheEI,
Amrhein2017TheEI,
goodman2008dirty,
greenland2016no,
Bernstein2016princess,
Trafimow2015ban,
Read2002cls
}
\TODO{examples of use and misuse in hep}

>>>>

% p-values
\TODO{no!}~\cite{
schervish1996p,
Cohen1994TheEI,
Amrhein2017TheEI,
goodman2008dirty,
greenland2016no,
Bernstein2016princess,
Trafimow2015ban,
wagenmakers2007practical,
Read2002cls
}
\TODO{examples of use and misuse in hep}
